DraftOne

### 2016-07-24 writing/JSSDraft/JSSDraft.Rmd
Summarizing Butland2013

>>>>

\citet{Butland2013} performed a simulation study to compare models using geographically resolved, simulated air pollution measures and air pollution concentrations averaged over geographic areas.  Recently, regional air pollution chemistry-transport models (CTMs) have been developed which can simulate air pollution concentrations over highly-resolved geographic areas.  These are useful where pollutants cannot be measured or can only be measured in a few locations.  The authors used simulation to investigate if and when it is better to use air pollution measurements from CTMs when estimating health outcomes rather than measures obtained from averaging over geographic grids based on monitor data.

The authors first simulated "true" values for pollutant concentrations over 100 grid squares, each with a specific mean concentration.  They generated daily values for each grid square over three years, including between-grid covariances.  Then they sampled the number of daily deaths from a poisson with mean dependent on the "true" concentrations.  Their generation of daily mortality counts could be done using eesim.  The authors then simulate  monitor data with classical measurement error and CTM data with both classical and Berkson error.  They separately fit the CTM data and regional averages from the monitor data to the simulated mortality counts and display several measures of model performance, including standard error of the estimates, coverage, and power, all of which can be produced using eesim.  Their results suggested that there may be a significant penalty in the form of increased bias in health effect estimates for the use of CTMs over monitors due to the additional measurement error.
